%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Lead}
    {EPAM Systems}
    {Zurich, Switzerland}
    {Oct. 2021 - Present}
    {
      \begin{cvitems}
        \item {Architected and led delivery of a Python workflow to scrape and parse SQL lineage from multiple analytics data warehouses, publishing results daily to Azure Purview so auditors can trace data from sources through to storage.}
        \item {Serves on internal expert assessment committees; mentors engineers and supports technical interviews.}
        \item {Led a team delivering a metadata synchronisation service connecting multiple systems and distributing metadata changes reliably, processing on the order of half a million records per day.}
        \item {Designed and implemented a Java adapter microservice exposing a mainframe SOAP service as a REST API so clients could integrate with standard HTTP-based tooling.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {JPMorgan Chase}
    {London, United Kingdom}
    {Sep. 2019 - Oct. 2021}
    {
      \begin{cvitems}
        \item {Built and launched a regulatory intraday liquidity dashboard with live metrics (WebSockets, React/Redux) and automated Excel reporting, streamlining workflows for 200+ business analysts.}
        \item {Optimized a high-volume messaging pipeline for 150K+ funding messages per hour, cutting publication time from 30 minutes to under five minutes using Apache Kafka and asynchronous processing.}
        \item {Delivered legacy account-balance offload work: Java thread pools, concurrency-safe versioning, and decommissioning of the previous system to improve maintainability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Summer Intern}
    {JPMorgan Chase}
    {London, United Kingdom}
    {Jun. 2018 - Sep. 2018}
    {
      \begin{cvitems}
        \item {Shipped features for regulatory tooling: dashboard work, live metrics, and TypeScript-driven Excel export; supported auditing workflows for internal analysts.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
